---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

baizer::pkglib(tidyverse, baizer)
```

# plutor

<!-- badges: start -->
[![R-CMD-check](https://github.com/william-swl/plutor/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/william-swl/plutor/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## installation

You can install the development version of `plutor` like so:

``` r
devtools::install_github("william-swl/plutor")
```
And load the package:
```{r library}
library(plutor)
```

## color

- select most distant colors among a color spectrum
```{r color-select_color}
select_color(5)
```

- generate gradient colors
```{r color-gradient_color}
gradient_color(c("blue", "red"), 10)
```

- show colors
```{r color-plot_col, fig.width=4, fig.height=3, dpi=300 }
plot_col(gradient_color(c("blue", "red"), 10))
```



## theme

- a custom flexible theme
```{r theme-theme_pl, fig.width=4, fig.height=3, dpi=300 }
ggplot(mini_diamond, aes(x = x, y = y, color = clarity)) +
  geom_point(size = 2) +
  facet_grid(. ~ cut) +
  labs(title = "title", tag = "tag", caption = "caption") +
  theme_pl()
```

- a blank theme
```{r theme-theme_pl0, fig.width=4, fig.height=3, dpi=300 }
ggplot(mini_diamond, aes(x = x, y = y, color = clarity)) +
  geom_point(size = 2) +
  facet_grid(. ~ cut) +
  labs(title = "title", tag = "tag", caption = "caption") +
  theme_pl0()
```


- a fixed mapping from size in `geom_xxx` to unit `pt` under 300 dpi
```{r theme-pt}
# for text and points
# geom_point(..., size = tpt(5))
# geom_text(..., size = tpt(5))

# for lines
# geom_line(..., linewidth = lpt(1))
```

- units transformation
```{r theme-units}
# inches <-> centimeters
inch2cm(1)
in2cm(1)
cm2inch(1)
cm2in(1)

# inches <-> millimeters
inch2mm(1)
in2mm(1)
mm2inch(1)
mm2in(1)

# points <-> centimeters
pt2cm(1)
cm2pt(1)

# points <-> millimeters
pt2mm(1)
mm2pt(1)
```


## IO
- save a plot
```{r IO-pl_save1}
# pl_save(p, 'plot.pdf', width=14, height=10)
```

- save a plot into an blank A4 canvas, or a custom canvas
```{r IO-pl_save2}
# pl_save(p, 'plot.pdf', width=14, height=10, canvas='A4', units='cm')

# pl_save(p, 'plot.pdf', width=14, height=10, canvas=c(20, 25), units='cm')
```

