---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

baizer::pkglib(tidyverse, baizer, badger)
```

# plutor

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/william-swl/plutor/branch/master/graph/badge.svg)](https://app.codecov.io/gh/william-swl/plutor?branch=master)
[![R-CMD-check](https://github.com/william-swl/plutor/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/william-swl/plutor/actions/workflows/check-standard.yaml)
`r badge_cran_release("plutor", "orange")`
`r badge_devel("william-swl/plutor", "blue")`
`r badge_cran_download("plutor", "grand-total", "blue")`
`r badge_cran_download("plutor", "last-month", "green")`
<!-- badges: end -->

- In ancient Roman mythology, `Pluto` was the ruler of the underworld and presides over the afterlife.

- `Pluto` was frequently conflated with `Plutus`, the god of wealth, because mineral wealth was found underground.

- When plotting with R, you try once, twice, practice again and again, and finally you get a pretty figure you want.

- It's a `plot tour`, a tour about repetition and reward.

- Hope `plutor` helps you on the tour!

## installation

You can install the development version of `plutor` like so:

``` r
devtools::install_github("william-swl/plutor")
```
And load the package:
```{r library}
library(plutor)
```

It is recommended to perform initialization, which adjusts the default plotting parameters in an interactive environment (such as jupyter notebook) and sets the default theme to `theme_pl()`.

```{r init}
pl_init()
```


## plots

Description values plot:

- The describe geom is used to create description values plot, including center symbol and error symbol.

- The center symbol can be mean, median or other custom functions.

- The error symbol can be sd, quantile or other custom functions.

```{r plots-geom_describe, fig.width=4, fig.height=3, dpi=300 }
mini_diamond %>% ggplot(aes(x = cut, y = price)) +
  geom_point() +
  geom_describe()
```

```{r plots-geom_describe_custom, fig.width=4, fig.height=3, dpi=300 }
center_func <- median
low_func <- function(x, na.rm) {
  quantile(x, 0.25, na.rm = na.rm)
}

high_func <- function(x, na.rm) {
  quantile(x, 0.75, na.rm = na.rm)
}

mini_diamond %>% ggplot(aes(x = cut, y = price)) +
  geom_point() +
  geom_describe(center_func = center_func, low_func = low_func, high_func = high_func)
```


Add p value and fold change on a plot

```{r plots-geom_point, fig.width=4, fig.height=3, dpi=300 }
p <- ggplot(data = mini_diamond, mapping = aes(x = cut, y = price)) +
  geom_point() +
  geom_compare(cp_label = c("psymbol", "right_deno_fc"), lab_pos = 25000, step_increase = 0.3) +
  ylim(0, 40000)
p
```


```{r plots-geom_point_inline, fig.width=4, fig.height=3, dpi=300 }
ggplot(data = mini_diamond, mapping = aes(x = cut, y = price)) +
  geom_point() +
  geom_compare(cp_ref = "Good", cp_inline = TRUE, lab_pos = 22000, brackets_widen = 0.1) +
  geom_compare(cp_ref = "Ideal", cp_inline = TRUE, lab_pos = 25000, brackets_widen = 0.1) +
  ylim(0, 40000)
```

extract the result of `geom_compare` from a `ggplot` object
```{r extract_compare}
head(extract_compare(p))
```

A new `Stat` class to add mean labels on a plot

```{r plots-StatMeanPL, fig.width=4, fig.height=3, dpi=300 }
mini_diamond %>% ggplot(aes(x = cut, y = price)) +
  geom_point() +
  geom_text(aes(label = price), stat = "meanPL")
```

A new `Stat` class to add count labels on a plot

```{r plots-StatCountPL, fig.width=4, fig.height=3, dpi=300 }
mini_diamond %>% ggplot(aes(x = cut, y = price)) +
  geom_point() +
  geom_text(aes(label = price), stat = "countPL")
```

A new `Stat` class to add custom function labels on a plot

```{r plots-StatFuncPL, fig.width=4, fig.height=3, dpi=300 }
lab_func <- function(x) {
  str_glue("mean = {round(mean(x))}\nn = {length(x)}")
}

mini_diamond %>% ggplot(aes(y = cut, x = price)) +
  geom_point() +
  geom_text(aes(label = price),
    stat = "funcPL",
    lab_func = lab_func, lab_pos = 25000
  ) +
  xlim(0, 30000)
```

A new `Position` function to create float x/y position

```{r plots-, fig.width=4, fig.height=3, dpi=300 }
mini_diamond %>% ggplot(aes(x = clarity, y = price)) +
  geom_point() +
  geom_text(aes(label = price),
    stat = "countPL",
    lab_pos = 20000, position = position_floatyPL()
  )
```


A variant of `scale_y_log10()` to show axis minor breaks and better axis labels

```{r plots-scale_y_log10_pl, fig.width=4, fig.height=3, dpi=300 }
mini_diamond %>% ggplot(aes(x = cut, y = price)) +
  geom_point() +
  geom_text(stat = "meanPL", lab_pos = 30000) +
  scale_y_log10_pl(show_minor_breaks = TRUE, limits = c(100, 100000))
```

A variant of `scale_y_continuous()` to show axis minor breaks

```{r plots-scale_y_continuous_pl, fig.width=4, fig.height=3, dpi=300 }
mini_diamond %>% ggplot(aes(x = cut, y = price)) +
  geom_point() +
  geom_text(stat = "meanPL", lab_pos = 25000) +
  scale_y_continuous_pl(limits = c(0, 40000), minor_break_step = 2500)
```


## color

- generate gradient colors
```{r color-gradient_colors}
gradient_colors(c("blue", "red"), 10)
```

- show colors
```{r color-plot_colors, fig.width=4, fig.height=3, dpi=300 }
plot_colors(gradient_colors(c("blue", "red"), 10))
```

- select colors from `RColorBrewer` package presets

```{r color-brewer_colors}
brewer_colors("Blues", 5) %>% plot_colors()
```

- select colors from `ggsci` package presets
```{r color-sci_colors}
sci_colors("npg", 5) %>% plot_colors()
```


- assign colors by a column in a tibble, for the convenience to 
use `scale_color_identity()`

```{r color-assign_colors}
assign_colors(mini_diamond, cut, colors = sci_colors("nejm", 8))
```

- colors of nucleotides and amino acids
```{r color-bioletter_colors}
# bioletter_colors
```



## theme

- a custom flexible theme
```{r theme-theme_pl, fig.width=4, fig.height=3, dpi=300 }
ggplot(mini_diamond, aes(x = x, y = y, color = clarity)) +
  geom_point(size = 2) +
  facet_grid(. ~ cut) +
  labs(title = "title", tag = "tag", caption = "caption") +
  theme_pl()
```

- a blank theme
```{r theme-theme_pl0, fig.width=4, fig.height=3, dpi=300 }
ggplot(mini_diamond, aes(x = x, y = y, color = clarity)) +
  geom_point(size = 2) +
  facet_grid(. ~ cut) +
  labs(title = "title", tag = "tag", caption = "caption") +
  theme_pl0()
```


- a fixed mapping from size in `geom_xxx` to unit `pt` under 300 dpi
```{r theme-pt}
# for text and points
# geom_point(..., size = ppt(5))
# geom_text(..., size = tpt(5))

# for lines
# geom_line(..., linewidth = lpt(1))
```

- set repr size and resolution
```{r theme-pl_size}
pl_size(w = 4, h = 3, res = 300)
```


- units transformation
```{r theme-units}
# inches <-> centimeters
inch2cm(1)
in2cm(1)
cm2inch(1)
cm2in(1)

# inches <-> millimeters
inch2mm(1)
in2mm(1)
mm2inch(1)
mm2in(1)

# points <-> centimeters
pt2cm(1)
cm2pt(1)

# points <-> millimeters
pt2mm(1)
mm2pt(1)
```



## IO
- save a plot
```{r IO-pl_save1}
# pl_save(p, 'plot.pdf', width=14, height=10)
```

- save a plot into an blank A4 canvas, or a custom canvas
```{r IO-pl_save2}
# pl_save(p, 'plot.pdf', width=14, height=10, canvas='A4', units='cm')

# pl_save(p, 'plot.pdf', width=14, height=10, canvas=c(20, 25), units='cm')
```

